A comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-08-10 manuscript/paper.Rmd

```{r}
add_stable(
  read_rds(figure_file("datasets.rds","02-dataset_characterisation"))[[params$table_format]], 
  "datasets", 
  "Real datasets used in this study."
)
```

@@

```{r}
add_stable(
  read_rds(figure_file(
    "samplers.rds",
    "02-dataset_characterisation/3-synthetic")
  )[[params$table_format]], 
  "samplers", 
  "Distributions from which each parameter in the thermodynamic model was sampled."
)
```

>>>>

```{r}
add_stable(
  read_rds(figure_file("datasets.rds","01-datasets/05-dataset_characterisation"))[[params$table_format]], 
  "datasets", 
  "Real datasets used in this study."
)
```

@@

```{r}
add_stable(
  read_rds(figure_file(
    "samplers.rds",
    "01-datasets/05-dataset_characterisation/3-synthetic")
  )[[params$table_format]], 
  "samplers", 
  "Distributions from which each parameter in the thermodynamic model was sampled."
)
```
